INTELLIGENT SYSTEMS

### 2021-03-30 paper_3.tex
update 3.3.1

>>>>

\subsection{THE PROPOSED COMPRESSION FRAMEWORK}
\subsubsection{Architecture of End-to-End Compression Framework}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
    \centering
    \caption{The proposed novel compression framework.}
    \label{fig:framework}
\end{figure}
As mentioned, the first \emph{ComCNN} convolutional network is used to generate 
a compact representation of the input image which preserves the structural 
information and facilitates the reconstruction of image in high quality. The 
second convolutional network, \emph{RecCNN}, is used to improve the quality of the 
decoded image. In particular:
\begin{enumerate}
    \item \emph{Compact Representation Convolutional Neural Network (ComCNN)}: 
    This network is made up of three weighted layers. The first layer is 
    used to perform the extraction and representation of patches from the 
    input image. 64 filters are used, each 3x3xc in size where c indicates 
    the number of image channels. Thanks to these filters, 64 feature maps 
    are generated. The second layer has the task of downscaling and improving 
    the features with convolutional operations having stride equal to 2 
    and 64 filters of 3x3x64 size. In the last layer, \emph{c} filters, of 3x3x64 
    size, are used to reconstruct the compact representation.
    \item \emph{Reconstruction Convolutional Neural Network (RecCNN)}: The layers 
    are identical to those of the \emph{ComCNN} network, unlike the number. To 
    speed up training, as well as performance, methods such as residual 
    learning and batch normalization \cite{0799924133} are used. Finally, the image will be upsampled to its original size, using a cubic interpolation.
\end{enumerate}
